### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit No Education Women

Women with no education follow a pattern consistent with son
preference with shorter spacing when they have only girls compared 
to when they have one or more sons, and the differences are often 
statistically significant as shown in Table \ref{tab:median_sex_ratio_low}.
Most of the women without education live in rural areas,
while there are relatively few urban women with no education.
There are especially very few urban women to based the third
and fourth spell results on, and I therefore focus on rural women.

Predicted median duration has increased over time within
each sex composition.
The exception is for the first spell, where there is little
change, and possibly even a small decline.
This decline may be the result of a combination of lower recall
error, increasing age at marriage, and better health.

The differences in duration across sex compositions increase with 
spell number.
For the second spell, the difference in median duration between
having a girl or a boy as the first-born are mostly between 0.5 and 1 
month, although it varies from a low of 0.2 months for rural women 
in 1995--2004 period to a high of 1.5 months
for urban women in the 1985--1994 period.
Focusing on rural women for the third spell, the difference is in
duration, on average, slightly over one month between only girls and only boys 
and the differences are statistically significant in all periods.
For rural women, the differences for the fourth spell are just below
two months, except for the 1972--1984 period, which is
also the only period where the difference is not statistically significant.

It is possible that remaining recall error is behind some of the
smaller differences in duration.
One example is the second spell in the 1995--2004 period, where there 
is only 0.2 months difference between duration after one girl and 
duration after one boy.
Similarly, the small difference for the fourth spell in the 1972--1984
period may be the result of recall error with a very high 
percentage of boys for women with three girls, despite no availability
of sex selection.

>>>>

Women with no education follow a pattern consistent with son
preference with shorter spacing when they have only girls compared 
to when they have one or more sons, and the differences are often 
statistically significant as shown in Table \ref{tab:median_sex_ratio_low}.
Most of the women without education live in rural areas,
whereas there are relatively few urban women with no education.
There are especially very few urban women to based the third
and fourth spell results on, and I therefore focus on rural women.

Predicted median duration has increased over time within
each sex composition.
The exception is for the first spell, where there is little
change, and possibly even a small decline.

The differences in duration across sex compositions increase with 
spell number.
For the second spell, the difference in median duration between
having a girl or a boy as the first-born are mostly between a half
and one month.
For the third spell, the difference in duration between only girls 
and only boys is, on average, slightly over one month and statistically 
significant in all periods.
The differences for the fourth spell are between two and three months, 
except for the 1972--1984 period, which is also the only period where 
the difference is not statistically significant.
